\documentclass[10pt,letterpaper]{article}

\usepackage[margin=0.5in, top=0.4in, bottom=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{parskip}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% Section formatting — bold, uppercase, with a rule underneath
\titleformat{\section}
  {\bfseries\normalsize\uppercase}
  {}
  {0em}
  {}
  [\vspace{-0.6em}\rule{\textwidth}{0.4pt}]
\titlespacing*{\section}{0pt}{0.6em}{0.3em}

% Compact lists
\setlist[itemize]{leftmargin=1.2em, topsep=1pt, itemsep=0pt, parsep=0pt}
\setlist[itemize,2]{leftmargin=1.2em, topsep=0pt, itemsep=0pt, parsep=0pt, label=$\circ$}

\newcommand{\entry}[2]{%
  \noindent\textbf{#1}\hfill #2\par\vspace{-1pt}%
}

\newcommand{\subentry}[2]{%
  \noindent\textit{#1}\hfill #2\par\vspace{1pt}%
}

\begin{document}

% ---------- HEADER ----------
\begin{center}
  {\LARGE \textbf{Dmitri Raoul Morales}}\\[3pt]
  dmitrimorales024@gmail.com \enspace$\cdot$\enspace 305-942-4152 \enspace$\cdot$\enspace 13951 SW 75 ST, Miami, FL 33183
\end{center}

\vspace{-0.2em}

% ---------- EXPERIENCE ----------
\section{Experience}

\entry{Associate Software Engineer}{July 2024 -- Present}
\subentry{The Walt Disney Company}{Orlando, Florida}
\begin{itemize}
  \item \textbf{DXT wAIfinder:}
  \begin{itemize}
    \item Engineered the \texttt{wai} CLI in Go to distribute rules, skills, agents, and commands into Cursor, Amazon Q Developer, and GitHub Copilot layouts, standardizing spec-driven development across DXT without locking teams to a single AI IDE.
    \item Doubled sprint velocity, increased test case coverage by 5x, and improved application quality through higher-fidelity documentation generated via the tooling.
  \end{itemize}
  \item \textbf{Figaro 2.0 (Minnie Van):}
  \begin{itemize}
    \item Led major platform refactors and shipped Figaro 2.0, reducing tech debt through documented, DRY patterns, static configuration, and improved session and caching strategies across the Minnie Van service.
    \item Grew into a PR review role as the team scaled, establishing quality gates and code standards across three offshore developers.
  \end{itemize}
  \item \textbf{Automated People Counter (APC):}
  \begin{itemize}
    \item Architected a greenfield Spring Boot service from the ground up, designing the AuroraDB schema and integrating APS sensors over SOAP with mTLS.
    \item Introduced Liquibase for schema lifecycle management. First greenfield Liquibase deployment to production.
    \item Delivered the first production ridership telemetry used for bus route planning and guest-experience decisions.
  \end{itemize}
  \item \textbf{Magic Mobile Express (Ticketing):}
  \begin{itemize}
    \item Built a Swift App Clip enabling Cast Members to convert emailed barcode media into MagicMobile passes saved directly to Apple Wallet, streamlining park-entry activation for Guests.
  \end{itemize}
\end{itemize}

\vspace{0.1em}
\entry{Software Engineer Professional Intern}{May 2023 -- July 2024}
\subentry{The Walt Disney Company}{Orlando, Florida}
\begin{itemize}
  \item \textbf{Figaro (Minnie Van):}
  \begin{itemize}
    \item Engineered a full-stack application across an Angular frontend and Java Spring Boot REST API backend to replace legacy SharePoint-hosted tooling for Cast scheduling, ride operations, and guest PII handling.
    \item Delivered the platform that became the single source of truth for Minnie Van operations, replacing a fragmented SharePoint workflow used across multiple Cast teams.
  \end{itemize}
\end{itemize}

\vspace{0.1em}
\entry{Software Engineer Professional Intern}{May 2022 -- August 2022}
\subentry{The Walt Disney Company}{Orlando, Florida}
\begin{itemize}
  \item Demonstrated cross-platform mobile development viability by designing and delivering a proof-of-concept Flutter application targeting both iOS-native and web from a single codebase, integrated with RESTful services and a GitHub Actions build pipeline via Visual Studio App Center.
\end{itemize}

\vspace{0.1em}
\entry{Undergraduate Researcher}{August 2023 -- 2024}
\subentry{Palmeri Lab, Duke University}{Durham, North Carolina}
\begin{itemize}
  \item \textbf{\href{https://pratt.duke.edu/news/preventing-childhood-hearing-loss-worldwide/}{mHealth Tymp}:}
  \begin{itemize}
    \item Advanced a low-cost tympanometer device by authoring Zephyr and C firmware for dynamic speaker control driven by ear-canal volume estimates, and by migrating the team's PCB design workflow to KiCad in partnership with industry collaborators.
  \end{itemize}
\end{itemize}

% ---------- EDUCATION ----------
\section{Education}

\entry{Duke University}{Durham, North Carolina}
\subentry{Bachelor of Arts and Engineering, Computer Science and Biomedical Engineering}{May 2024}
\begin{itemize}
  \item GPA: \textbf{3.81 / 4.00} \enspace$\cdot$\enspace \textbf{2020} FAITH Endowment Scholar \enspace$\cdot$\enspace \textbf{2021--2023} FAITH Endowment STEM Scholar of Special Distinction
\end{itemize}

% ---------- LEADERSHIP ----------
\section{Leadership}

\begin{itemize}
  \item \textbf{FIRST Tech Challenge --- Team Vanta 31000:} Mentor for competitive robotics; team qualified for Worlds; recognized by Orlando Mayor Buddy Dyer for the achievement.
  \item Builds Godot game projects for applied engineering practice.
\end{itemize}

% ---------- SKILLS ----------
\section{Skills}

\textbf{Technologies:} Java, Spring Boot, Angular, TypeScript, Go, Python, Flutter, Swift, C, SQL, REST, SOAP, mTLS, Liquibase, Git, GitHub Actions, Visual Studio App Center, KiCad, Zephyr, PyTorch\\[2pt]
\textbf{Languages:} English (Native), Greek (Fluent)

\end{document}
